%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Huy A. Nguyen
\documentclass[margin,line]{resume}

%\vspace{-1.5mm}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Huy A. Nguyen}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    Wireless Research System Group                              \hfill office: +1 713 440-0054          \vspace{0mm}\\\vspace{0mm}%
    Department of Computer Science                              \hfill mobile: +1 832 446-7711         \vspace{0mm}\\\vspace{0mm}%
    University of Houston                                       \hfill nahuy@cs.uh.edu
    \vspace{0mm}\\\vspace{0mm}%
    Houston, Texas 77204                                        \hfill http://www2.cs.uh.edu/$\sim$nahuy/ \vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Science}, VNUHCM, Ho Chi Minh City, Vietnam
    \hfill \textbf{ Sep. 2002 -- Sep. 2006}\vspace{-3mm}\\\vspace{-1mm}%
    \\\vspace{1mm}%
    \textsl{Bachelor of Science in Computer Science}
    \begin{list2}
        \item Specialized in software engineering
    \end{list2}\vspace{-1.5mm}

    \textbf{Chonnam National University}, Gwangju, South Korea
    \hfill \textbf{ Mar. 2007 -- Mar. 2009}\vspace{-3mm}\\\vspace{-1mm}%
    \\\vspace{1mm}%
    \textsl{Master of Engineering in ECE}
    \begin{list2}
        \item Research interests: network management, anomaly and intrusion detection
        \item Advisor:  Prof. Deokjai Choi
    \end{list2}\vspace{-1.5mm}

    \textbf{University of Houston}, Houston, Texas
    \hfill \textbf{ Aug. 2009 -- present}\vspace{-3mm}\\\vspace{-1mm}%
    \\\vspace{1mm}%
    \textsl{Doctor of Philosophy in Computer Science}
    \begin{list2}
        \item Expected graduation date: 2013
        \item Advisor:  Dr. Rong Zheng
    \end{list2}%\vspace{3mm}


    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    Wireless and sensor network, network tomography, approximation algorithm, binary independent component analysis, convex optimization.\vspace{-1.5mm}

%    Service predictability in networked systems, convex optimization and applications, network management, anomaly and intrusion detection.\\\vspace{-1.5mm}


    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{ELCA Information Technology}, Ho Chi Minh City, Vietnam \vspace{0mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{Sep. 2006 -- Feb. 2007}\\\vspace{-4mm}
    \begin{list2}
        \item Software development with Java and Oracle
        \item Web application development with PHP and MySQL
    \end{list2}\vspace{-1.5mm}

    \textbf{Chonnam National University}, Gwangju, South Korea \vspace{0mm}\\\vspace{1mm}%
    \textsl{Research Assistant} at Advanced Network Lab \hfill \textbf{Mar. 2007 -- Feb. 2009}\vspace{-2.5mm}

    \textbf{University of Houston}, Houston, Texas \vspace{0mm}\\\vspace{0mm}%
    \textsl{Teaching Assistant} at Computer Science Department \hfill \textbf{Aug. 2009 -- Dec. 2009}\\
    \textsl{Research Assistant} at Wireless Research System Group \hfill \textbf{Jan. 2010 -- present}\\\vspace{-5mm}

    %__________________________________________________________________________________________________________________
    % Programming Languages
    \section{\mysidestyle Programming\\Languages}

    Pascal, Fortran, Matlab, C/C++, C\#, Java, ASP.NET, PHP, JSP, HTML, CSS, XML, SQL.\vspace{1.5mm}

    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Selected Publications}

    Arun Chhetri, Huy Nguyen, Gabriel Scalosub, and Rong Zheng,
    ``On Quality of Monitoring for Multi-channel Wireless Infrastructure Networks'',
    In \textsl{Proc. of The 11th Mobihoc}, September 20-24, Chicago, Illinois, USA, 2010.

    \vspace{-2mm}
    Huy Nguyen, Rong Zheng, and Zhu Han,
    ``Binary is Good: A Binary Inference Framework for Primary User Separation in Cognitive Radio Networks'',
    In \textsl{Proc. of The 5th CrownCom}, June 9-11, Cannes, France, 2010.

    \vspace{-2mm}
    Huy Nguyen, Tam Van Nguyen, and Deokjai Choi,
    ``How to Maximize User Satisfaction Degree in Multi-services IP Networks'',
    In \textsl{Proc. of The 1st ACIIDS}, April 1-3, Quang Binh, Vietnam, 2009.

    \vspace{-2mm}
    Huy Nguyen and Deokjai Choi,
    ``Application of Data Mining to Network Intrusion Detection: Classifier Selection Model'',
    In \textsl{Proc. of The 11th APNOMS}, October 22-24, Beijing, China, 2008.

    \vspace{-2mm}
    Huy Nguyen, Tam Van Nguyen, Dongil Kim, and Deokjai Choi,
    ``Network Traffic Anomalies Detection and Identification with Flow Monitoring'',
    In \textsl{Proc. of The 5th WOCN}, May 5-7, Surabaya, Indonesia, 2008.\\\vspace{-5mm}


    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards}

    Excellent Student of The University of Natural Sciences, 2002 to 2006                           \vspace{1mm}\\%
    Learning Encouraging Scholarship of The University of Natural Sciences, 2002 to 2006            \vspace{1mm}\\%
    TMA scholarship for HCMUNS Computer Science Students, 2006                                      \vspace{1mm}\\%
    HCMUNS Roll of Honor, 2006                                                                      \vspace{1mm}\\%
    Institute of Information Technology Assessment (IITA) Scholarship, 2007 to 2008                 \vspace{1mm}\\%
    Chonnam National University Global Scholarship, 2009                                            \vspace{1mm}\\%
    Chonnam National University BK21 Scholarship, 2009                                              \vspace{1mm}\\%
    ACM MobiCom/MobiHoc 2010 Student Travel Grants 2010

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

